\textit{Supporting Information for}: Geometric models reveal behavioral and neural signatures of how naturalistic experiences are transformed into episodic memories

### 2020-08-18 paper/supporting_information.tex

\title{\textit{Supporting Information for}: Geometric models reveal behavioral and neural signatures of how naturalistic experiences are transformed into episodic memories}
\author{Andrew C. Heusser\textsuperscript{1, 2, \textdagger}, Paxton C. Fitzpatrick\textsuperscript{1, \textdagger}, and Jeremy R. Manning\textsuperscript{1, *}\\\textsuperscript{1}Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\\textsuperscript{2}Akili Interactive\\Boston, MA 02110\\\textsuperscript{\textdagger}Denotes equal contribution\\\textsuperscript{*}Corresponding author: jeremy.r.manning@dartmouth.edu}

>>>>

\title{\textit{Supporting Information for}: Geometric models reveal behavioral and neural signatures of how naturalistic experiences are transformed into episodic memories}
\author{Andrew C. Heusser\textsuperscript{1, 2, \textdagger}, Paxton C. Fitzpatrick\textsuperscript{1, \textdagger}, and Jeremy R. Manning\textsuperscript{1, *}\\\textsuperscript{1}Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\\textsuperscript{2}Akili Interactive\\Boston, MA 02110\\\textsuperscript{\textdagger}Denotes equal contribution\\\textsuperscript{*}Corresponding author: Jeremy.R.Manning@dartmouth.edu}
